\textbf{COMP0086 Summative Assignment}

### 2022-11-06 main.tex
add plots to tex file and big fix for q1b table orientation

\documentclass[12pt]{article}
\usepackage[paper=letterpaper,margin=2cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{newtxtext, newtxmath}
\usepackage{enumitem}
\usepackage{titling}
\usepackage[colorlinks=true]{hyperref}

@@

\begin{document}
\begin{enumerate}[leftmargin=\labelsep]
\item[8.]

\item[9.]
    \begin{enumerate}
        \item 
        let $K_{c}(\textbf{x},\textbf{z}) = c+ \sum_{i=1}^{n}x_{i}z_{i} = c + \textbf{x}^{T}\textbf{z}$\\
        Our function $K_{c}(\cdot, \cdot)$ is psd iff:\\
        $\forall \{ u_{i} \}_{1:m} \in \mathcal{R},
         \{ \textbf{x}_{j}\}_{1:m} \in \mathcal{R}^{n}$:

@@

    We note that as c becomes large, $\alpha \to 0$ and hence the predictions for $\hat{y}_{test}$ approach    
    the constant function $f(x) = lc$
    \\
    \newpage

    \item
    Define $g(t) := $sgn$(f(t)) = \frac{f(t)}{| f(t)|}$\\
    \textbf{Proposition:}\\

@@

    Note for $d_{i} \ne d_{*}$, $exp(-\beta(d_{i} - d_{*})) \to 0$ as $\beta \to \infty$. Hence:\\
    $g(t) \to \frac{y_{*}}{|y_{*} + 0|} + \frac{0}{|y_{*} + 0|} = y_{*} = y_{i} : x_{i} = min_{i} \|x_{test} - x_{i}\|$ which is the required 1-NN predictor.\\$
    \square$
    \item
    Given a whack-a-mole grid of size n, it is solvable if we can apply a sequence from our $n^{2}$ permissible moves that results in a blank screen. We first index all permissible moves by $T_{i,j}$, which has the effect of flipping the state of squares $(i,j),(i-1,j),(i+1,j),(i,j-1)(i,j+1)$, as long as each coordinate is still on the grid.\\
    We may consider each grid as an element of the space of square matrices over $\mathcal{F}_{2}$, the finite field of order 2: under this construction, we see that the application of a move $T_{i,j}$ corresponds to the sum between the grid and a matrix $T_{ij}$, where $T_{ij}$, where the entries of $T_{ij}$ are zero everywhere except at $(i,j),(i-1,j),(i+1,j),(i,j-1)(i,j+1)$, if these values are present on the grid. For example, if n = 4, the transformation $T_{2,2}$ corresponds to the addition of the matrix $T_{22}$:\\

@@

    \end{enumerate}
\item

>>>>

\documentclass[12pt]{article}
\usepackage[paper=letterpaper,margin=2cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{newtxtext, newtxmath}
\usepackage{enumitem}
\usepackage{titling}
\usepackage[colorlinks=true]{hyperref}
\usepackage{graphicx}
\usepackage{csvsimple}

@@

\title{\textbf{COMP0086 Summative Assignment}}
\author{Alexei Pisacane and Jian Shu (James) Wu \\ }
\date{Nov 16, 2022}

\begin{document}
    \maketitle
\begin{enumerate}[leftmargin=\labelsep]
\section{PART I}
\subsection{Linear Regression}
\item[1.]
    \begin{enumerate}
        \item Superimposing the four different curves corresponding to each fit over the four given data points:
        \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.5]{outputs/python/q1/q1a}
        \caption{Data set $\{(1, 3), (2, 2), (3, 0), (4, 5)\}$ fitted with basis $\{1, x\}$ and basis $\{1, x, x^2, x^3\}$ }
        \label{fig:1a}
        \end{figure}

        \item The weights for the equations:
        \begin{center}
        \begin{tabular}{c|c|c|c|c}%
         \textbf{Basis}&\textbf{k=1}&\textbf{k=2}&\textbf{k=3} &\textbf{k=4}% specify table head
        \csvreader[head to column names]{outputs/python/q1/q1b.csv}{}% use head of csv as column names
        {\\\hline\csvcoli&\csvcolii&\csvcoliii&\csvcoliv&\csvcolv}% specify your coloumns here
        \end{tabular}
        \end{center}

        \item The mean squared error for each fitted curve:
        \begin{center}
        \begin{tabular}{c|c|c|c|c}%
         \textbf{Metric}&\textbf{k=1}&\textbf{k=2}&\textbf{k=3} &\textbf{k=4}% specify table head
        \csvreader[head to column names]{outputs/python/q1/q1c.csv}{}% use head of csv as column names
        {\\\hline\csvcoli&\csvcolii&\csvcoliii&\csvcoliv&\csvcolv}% specify your coloumns here
        \end{tabular}
        \end{center}
    \end{enumerate}
\newpage
\item[2.]
    \begin{enumerate}
        \item
        \begin{enumerate}
            \item Superimposing the function $sin^2(2\pi x)$ in the range $0 \leq x \leq 1$ with the points of the above data set superimposed
                    \begin{figure}[h]
                    \centering
                    \includegraphics[scale=0.5]{outputs/python/q2/q2ai}
                    \caption{Noisy samples}
                    \label{fig:2ai}
                    \end{figure}
            \item Fitting the data set with a polynomial bases of dimension $k = 2, 5, 10, 14, 18$ and plotting each of these 5 curves superimposed over a plot of data points:
                    \begin{figure}[h]
                    \centering
                    \includegraphics[scale=0.5]{outputs/python/q2/q2aii}
                    \caption{Polynomial fit curves}
                    \label{fig:2aii}
                    \end{figure}
        \end{enumerate}
\newpage
        \item Plotting  the natural $\log$ ($\ln$) of the training error versus the polynomial dimension $k = 1, . . . , 18$:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q2/q2b}
            \caption{Training Error of Polynomial Curves}
            \label{fig:2b}
            \end{figure}

        \item Plotting the $\ln$ of the test error for a single trial of 1000 test points versus the polynomial dimension $k = 1, . . . , 18$:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q2/q2c}
            \caption{Testing Error of Polynomial Curves (1 trial)}
            \label{fig:2c}
            \end{figure}
\newpage
        \item Plotting the $\ln$ of the test error for 100 trials of 1000 test points versus the polynomial dimension $k = 1, . . . , 18$:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q2/q2d}
            \caption{Testing Error of Polynomial Curves (100 trials)}
            \label{fig:2d}
            \end{figure}
    \end{enumerate}
\newpage
\item[3.] Repeating 2 (b-d) with $\sin$ basis functions:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q3/q3b}
            \caption{Training Error of $\sin$ Curves}
            \label{fig:3b}
            \end{figure}
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q3/q3c}
            \caption{Testing Error of $\sin$ Curves (1 trial)}
            \label{fig:3c}
            \end{figure}
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q3/q3d}
            \caption{Testing Error of $\sin$ Curves (100 trials)}
            \label{fig:3d}
            \end{figure}
\newpage
\subsection{Filtered Boston housing and kernels}
\item[4.]
\newpage
\subsection{Kernelised ridge regression}
\item[5.]
\newpage
\section{PART II}
\subsection{$k$-Nearest Neighbors}
\item[6.]Generating a random $h$:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q6/q6}
            \caption{A hypothesis $h_{S,v}$ visualised with $|S|=100$ and $v=3$}
            \label{fig:6a}
            \end{figure}
\newpage
\item[7.]
    \begin{enumerate}
        \item Producing a visualisation using Protocol A:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q7/q7}
            \caption{Protocol A}
            \label{fig:7}
            \end{figure}
        \item TODO
    \end{enumerate}
\newpage
\item[8.]
    \begin{enumerate}
        \item Producing a visualisation using Protocol B:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q8/q8}
            \caption{Protocol B}
            \label{fig:8}
            \end{figure}
        \item TODO
    \end{enumerate}
\newpage
\section{PART III}
\subsection{Questions}
\item[9.] \begin{enumerate}
              \item let $K_{c}(\textbf{x},\textbf{z}) = c+ \sum_{i=1}^{n}x_{i}z_{i} = c + \textbf{x}^{T}\textbf{z}$\\
        Our function $K_{c}(\cdot, \cdot)$ is psd iff:\\
        $\forall \{ u_{i} \}_{1:m} \in \mathcal{R},
         \{ \textbf{x}_{j}\}_{1:m} \in \mathcal{R}^{n}$:

@@

    We note that as c becomes large, $\alpha \to 0$ and hence the predictions for $\hat{y}_{test}$ approach
    the constant function $f(x) = lc$
\end{enumerate}

\newpage
\item[10.]  Define $g(t) := $sgn$(f(t)) = \frac{f(t)}{| f(t)|}$\\
    \textbf{Proposition:}\\

@@

    Note for $d_{i} \ne d_{*}$, $exp(-\beta(d_{i} - d_{*})) \to 0$ as $\beta \to \infty$. Hence:\\
    $g(t) \to \frac{y_{*}}{|y_{*} + 0|} + \frac{0}{|y_{*} + 0|} = y_{*} = y_{i} : x_{i} = min_{i} \|x_{test} - x_{i}\|$ which is the required 1-NN predictor.\\$
    \square$
\newpage
\item[11.] Given a whack-a-mole grid of size n, it is solvable if we can apply a sequence from our $n^{2}$ permissible moves that results in a blank screen. We first index all permissible moves by $T_{i,j}$, which has the effect of flipping the state of squares $(i,j),(i-1,j),(i+1,j),(i,j-1)(i,j+1)$, as long as each coordinate is still on the grid.\\
    We may consider each grid as an element of the space of square matrices over $\mathcal{F}_{2}$, the finite field of order 2: under this construction, we see that the application of a move $T_{i,j}$ corresponds to the sum between the grid and a matrix $T_{ij}$, where $T_{ij}$, where the entries of $T_{ij}$ are zero everywhere except at $(i,j),(i-1,j),(i+1,j),(i,j-1)(i,j+1)$, if these values are present on the grid. For example, if n = 4, the transformation $T_{2,2}$ corresponds to the addition of the matrix $T_{22}$:\\

@@
